Quality Definitions of Qualities

### 2019-10-23 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Correctness definitions - fixed formatting as definitions, natbib citations, added new def

\subsection{Correctness}
\begin{itemize}
	\item{Definition 1:} The degree to which a software's specification is satisfied (\cite{berander2005software}).\\
	\item{Definition 2:} A software is correct if it functions according to its specified functional and non-functional specification(\cite{GhezziEtAl2003})\\.
	\item{Definition 3:} According to \cite{wilson2009quality}, ``the degree to which a system is free from defects in its specification, design, and implementation, is its correctness.\\
	\item{Definition 4:} ``The ability of software products to perform their exact tasks, as defined by their specification'' (\cite{meyer1988object}). \\
	\item{\textbf{Proposed definition}:} Definition 2
\end{itemize}

>>>>

\subsection{Correctness}

\begin{defn}
  The degree to which a software's specification is satisfied
  \citep{berander2005software}.
\end{defn}

\begin{defn} \label{CorrectDefnSelected}
  A software is correct if it functions according to its specified functional
  and non-functional specification \cite{GhezziEtAl2003}.
\end{defn}

\begin{defn}
  According to \citet{wilson2009quality}, ``the degree to which a system is free
  from defects in its specification, design, and implementation, is its
  correctness.''
\end{defn}

\begin{defn}
  ``The ability of software products to perform their exact tasks, as defined by
  their specification'' \citep{meyer1988object}.
\end{defn}

\begin{defn}
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}.
\end{defn}

\noindent \textbf{Proposed definition}: Definition~\ref{CorrectDefnSelected}
